Abstract Data Type Inference

### 2015-03-16 histories.tex
some small stuff

\section{Histories of ADT Implementations}
\label{sec:histories}

@@

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum number of
its operations which are mutually unordered, and the \emph{width} of a history
set is the maximum width of its elements. Width-$1$ histories are
\emph{sequential}.
Two operations $o, o'$ are \emph{identical}, written $o \sim o'$, when they
have the same labels: $c(o) = c(o')$, $f(o) = f(o')$, and matching: $m(o) =
m(o')$. The \emph{frequency} of an operation $o$ is the number $\freq(o) =
|\set{ o' \in O : o \sim o' }|$ of operations identical to $o$, and $o$ has
\emph{duplicates} when $\freq(o) > 1$. An operation $o \in \rng(m)$ is a
\emph{match target}, and the set $\set{ o' \in O : m(o') = o}$ of operations
targeting $o$ is a \emph{match}. We assume targets target themselves: $m(o) =
o$ for $o \in \rng(m)$. The \emph{weight} of $h$ is the maximum $\max(\set{
\freq(o) : o \in O } \cup \set{|\rng(m)|})$ between operation frequencies and
the number of matches. Since the operation identifiers of a history have no
intrinsic meaning, we consider equality between histories up to renaming of
operation identifiers.

>>>>

%!TEX root = draft.tex
\section{Histories of ADT Implementations}
\label{sec:histories}

@@

\end{itemize}
Non-completed operations are \emph{pending}, and are maximal in the
happens-before order. The \emph{width} of a history is the maximum number of
its operations which are mutually unordered, and the \emph{width} of a history
set is the maximum width of its elements. Width-$1$ histories are
\emph{sequential}.
Two operations $o, o'$ are \emph{identical}, written $o \sim o'$, when they
have the same labels: $c(o) = c(o')$, $f(o) = f(o')$, and matching: $m(o) =
m(o')$ (TODO: if matching is defined).

The \emph{frequency} of an operation $o$ is the number $\freq(o) =
|\set{ o' \in O : o \sim o' }|$ of operations identical to $o$, and $o$ has
\emph{duplicates} when $\freq(o) > 1$. An operation $o \in \rng(m)$ is a
\emph{match target}, and the set $\set{ o' \in O : m(o') = o}$ of operations
targeting $o$ is a \emph{match}. We assume targets target themselves: $m(o) =
o$ for $o \in \rng(m)$. The \emph{weight} of $h$ is the maximum $\max(\set{
\freq(o) : o \in O } \cup \set{|\rng(m)|})$ between operation frequencies and
the number of matches. Since the operation identifiers of a history have no
intrinsic meaning, we consider equality between histories up to renaming of
operation identifiers.
